Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-03 WSSSPE1_report/WSSSPE1_summary_report.tex
small change

% TODO: Why are we doing case studies?
In this section, we discuss some of the software projects as case-studies to
better understand the points discussed during the workshop and described in the
previous sections. We dive deeper to find how are they affected by the
sustainability issues in practice.

@@

% Below: What are the goals of this discussion? TODO: Better motivate. May be make a brief list of items discussed in the workshop.
We aim to understand the practicalities of the key points discussed in the
workshop, and hope to extract the best practices associated with the case
studies. We discuss how the issues are applicable to the cases and try to
understand how the course of current and future development projects might be
altered to implement lessons learned. We discuss vatious issues including
career paths of original developers and investigate if the original developers
are still around?

>>>>

In this section, we discuss some of the software projects as case-studies to
better understand the points discussed during the workshop and described in the
previous sections. We dive deeper to find how are they affected by the
sustainability issues in practice.

@@

% Below: What are the goals of this discussion? TODO: Better motivate. May be make a brief list of items discussed in the workshop.
We aim to understand the practicalities of the key points discussed in the
workshop, and discuss the practices associated with the use-cases. We discuss
how the issues are applicable to the cases and try to understand how the course
of current and future development projects might be altered to implement
lessons learned. We discuss various issues including career paths of original
developers and investigate if the original developers are still around?
